---
title: "Usage of the Package magickx"
author: "Hauke Sonnenberg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage of the Package magickx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Load the Packages

```{r}
library(magick)
library(magickx)
```

## Load Example Images

```{r}
# Define a Helper Function to Create URLs
image_URLs <- function(day_string, hours = 0:23) file.path(
  "http://wind.met.fu-berlin.de/loops/bwb", 
  sprintf("BWBRR_TEXT_%s_%02d00.gif", day_string, hours)
)

yesterday <- gsub("-", "", Sys.Date()-1)

# Define different sets of URLs
urls_1 <- image_URLs(day_string = yesterday, 8:10)
urls_2 <- image_URLs(day_string = yesterday, 13:23)

# Show some URLs
head(urls_1)
```

### Read Images from URLs

With the `image_read()` function of the `magick` package you can read images 
from many files or URLs in one function call. This function stops if there is
at least one path or URL from which no image could be read. The package
`magickx` contains a function `try_image_read()` that does not stop on errors
but skips files that do not exist or from which no image can be read and prints
out the corresponging error messages.

#### Read with `image_read()` from the `magick` package

```{r error = TRUE, collapse = TRUE}
# Try to read the images
images <- image_read(urls_1)

# How many images have been read?
length(images)
```

The execution stops, so that the variable `images` is not created.

#### Read with `try_image_read()` from the `magickx` package

```{r collapse = TRUE}
# Try to read the images
images <- try_image_read(urls_1)

# How many images have been read?
length(images)
```

Error messages are shown but the function completes. The variable `images` now
contains `r (n1 <- length(images))` images (`r (n2 <- length(urls_1))` were
requested, `r (n <- n2 - n1)` `r ifelse(n > 1, "were", "was")` skipped). 
For the following examples, we will download images from the second set of URLs
(`urls_2`). This works without any error:

```{r}
images <- try_image_read(urls_2)
```

## Show Example Images

The variable `images` is a vector of `r length(images)` images. If you print 
them, they will be overlayed:

```{r}
print(images)
```

Use `image_animate()` from the `magick` package to show them one after each
other in a short animation:

```{r}
image_animate(images, fps = 2)
```

## Define Crop Areas

```{r}
# Define path to file in the package containing crop information
file <- system.file("extdata/crop_info.csv", package = "magickx")

# Load the crop information from the file
crop_info <- read.table(file, stringsAsFactors = FALSE)

# Specify rows of interest
row_names <- c("DateTime", grep("^bwb[0:1]", rownames(crop_info), value = TRUE))

# Select the geometry strings of rows of interest and name them
geometries <- setNames(crop_info[row_names, "geometry"], row_names)

# Show the geometry strings
geometries
```

## Create Columns from Cropped Parts of the Images

```{r eval = TRUE}
# Crop area "DateTime" in each image and append the areas vertically
image_matrix(image_crop(images, geometries["DateTime"]))

# Crop area "bwb15" in each image and append the areas horizontally
image_matrix(image_crop(images, geometries["bwb15"]), nrow = 1)
```

## Append Image Columns Next to Each Other

```{r eval = TRUE}
# Use all geometries to crop areas, append them vertically and append the
# resulting column images horizontally
gauge_images <- lapply(geometries, image_crop, image = images)

# Number of columns in image matrix to be created
n_col <- length(gauge_images)

# Arrange vector of images in a matrix
page_image <- image_matrix(list_to_magick(gauge_images), ncol = n_col)

# Show the resulting image
page_image
```

## Extract Rows or Columns of an Image

```{r}
# Select rows and columns "positively"
page_image[1:5, 1:10]
page_image[1:2, ]
page_image[, c(1, 3, 5)]

# Exclude rows or columns with negative indices
page_image[-seq(1, nrow(page_image), by = 2), -c(9:10, 18)]
```

```{r echo = FALSE}
#border <- c(10, 10)
#widths  <- crop_info[, "width"] + border[1]
#heights <- crop_info[, "height"] + border[2]
```
