---
title: "Usage of the Package magickx"
author: "Hauke Sonnenberg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage of the Package magickx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Load the Packages

```{r}
library(magick)
library(magickx)
```

## Load Example Images

### Define a Helper Function to Create URLs

```{r}
to_image_url <- function(day_string, hours = 0:23) file.path(
  "http://wind.met.fu-berlin.de/loops/bwb", 
  sprintf("BWBRR_TEXT_%s_%02d00.gif", day_string, hours)
)
```

### Define URLs

```{r}
# Define different sets of URLs
urls_1 <- to_image_url(day_string = "20180417")
urls_2 <- to_image_url(day_string = "20170103")

# Show some URLs
head(urls_1)
head(urls_2)
```

### Read Images from URLs

With the `image_read()`-function of the `magick` package you can read images 
from many files or URLs in one function call. This function stops if there is
any path or URL from which no image could be read. The package `magickx` 
contains a function `try_image_read()` that does not stop on errors but skips 
the file that cannot be read and prints an error message. 

Using `image_read()` stops with an error:

```{r error = TRUE}
images <- magick::image_read(urls_1)
```

Nothing was assigned to the variable `images`:

```{r error = TRUE}
length(images)
```

Using `try_image_read()` shows the error message but continues:

```{r}
images <- magickx::try_image_read(urls_1) # All files can be read
```

The variable `images` now contains two (out of three) images (one was skipped):

```{r}
length(images)
```

For the following examples, we will download images from the second set of URLs
`urls_2` (without any error):

```{r}
images <- try_image_read(urls_2)
```

## Show Example Images

The variable `images` is a vector of three images. If you print them, they will
be overlayed:

```{r}
print(images)
```

Use the function `image_append` from the `magick` package to arrange the images
on top of each other (here only the first two):

```{r}
image_append(images[1:2], stack = TRUE)
```

## Define Crop Areas

```{r}
# Define path to file in the package containing crop information
file <- system.file("extdata/crop_info.csv", package = "magickx")

# Load the crop information from the file
crop_info <- read.table(file)

# Select rows of interest0
row_names <- c("DateTime", grep("^bwb[0:1]", rownames(crop_info), value = TRUE))
crop_info <- crop_info[row_names, ]

# Show the crop information
crop_info
```

## Convert Crop Area Information to Geometry Strings

```{r}
geometries <- apply(crop_info, 1, function(x) geometry_area(
  
  x["width"], x["height"], x["x_off"], x["y_off"]
))

# Show the geometry strings
geometries
```

## Create Columns from Cropped Parts of the Images

```{r eval = TRUE}
# Crop area "DateTime" in each image and append the areas vertically
crop_to_column(images, geometries["DateTime"])

# Crop area "bwb15" in each image and append the areas horizontally
crop_to_row(images, geometries["bwb15"])
```

## Append Image Columns Next to Each Other

```{r eval = TRUE}
# Use all geometries to crop areas, append them vertically and append the
# resulting column images horizontally
page_image <- crop_to_column(images, geometries)

# Show the resulting image
page_image
```

## Select Rows or Columns from an Image

```{r}
# Select rows and columns
extract(page_image, 1:10, 1:10)

# Exclude rows or columns with negative indices
image <- extract(page_image, -(5:15), -c(9:10, 18))
```

The same result as above can be achieved like this:

```{r}
gauge_images <- lapply(geometries, image_crop, image = images)

# Arrange vector of images in a matrix
image_matrix(list_to_magick(gauge_images), ncol = length(gauge_images))
```

```{r echo = FALSE}
#border <- c(10, 10)
#widths  <- crop_info[, "width"] + border[1]
#heights <- crop_info[, "height"] + border[2]
```
